---
title: "Network comparison: `r params$label_b` vs `r params$label_a`"
output:
  html_document:
    toc: true
    toc_float: true
params:
  analysis_a: "baseline"
  analysis_b: "risk_adjusted"
  label_a: "baseline"
  label_b: "risk-factor-adjusted"
  results_dir_a: "../results"
  results_dir_b: "../results"
  attribution: true
  overlap: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10)
source("../R/analysis_functions.R")
ma <- read_model(file.path(params$results_dir_a, "models", params$analysis_a),
                 file.path(params$results_dir_a, "sequences", params$analysis_a))
mb <- read_model(file.path(params$results_dir_b, "models", params$analysis_b),
                 file.path(params$results_dir_b, "sequences", params$analysis_b))
# compare over the cardiometabolic (CMD) event types
A <- cmd_submatrix(ma); B <- cmd_submatrix(mb)
cmp <- compare_networks(A, B)
```

Comparison of the CMD-to-CMD excitation matrices of **`r params$label_b`**
(B) and **`r params$label_a`** (A); differences are B minus A. For models with
CMD and risk-factor events, the CMD-to-CMD submatrix is used.

## Networks

```{r}
knitr::kable(rbind(cbind(network = params$label_a, network_summary(A)),
                   cbind(network = params$label_b, network_summary(B))))
```

## Element-wise differences

Pearson correlation of edge strengths, direction of change, and two-sided
Wilcoxon signed-rank test on the element-wise differences (pairs with zero
difference are excluded by the test; `signed_rank_n` is the effective sample
size). Substantially altered pairs: absolute difference above the 95th
percentile of the non-zero absolute differences.

```{r}
knitr::kable(t(cmp$stats[, lapply(.SD, signif, 4)]), col.names = "value")
```

```{r, fig.height = 9}
plot_difference(cmp$diff, sprintf("Difference in\nexcitation strength\n(%s minus\n%s)", params$label_b, params$label_a))
```

### Substantially altered pairs

```{r}
knitr::kable(cmp$altered, digits = 4)
```

```{r, eval = isTRUE(params$attribution), results = "asis"}
cat("## Risk-factor excitation and shared risk-factor attribution\n\n")
map <- mb$mapping
R <- mb$A[map$event_name[map$group == "RISK"], map$event_name[map$group == "CMD"]]
cat("### Ten strongest relationships from risk-factor event types to CMD events\n\n")
print(knitr::kable(top_edges(R, 10)))
att <- risk_attribution(mb, cmp$altered)
cat("\n\n### Shared risk-factor exposure: altered vs unaltered pairs (two-sided Wilcoxon rank-sum test)\n\n")
print(knitr::kable(att$test[, lapply(.SD, signif, 4)]))
cat("\n\n### Main shared risk factor of each substantially altered pair\n\n")
print(knitr::kable(att$pairs[altered == TRUE][order(min_score)], digits = 2))
```

```{r, eval = isTRUE(params$overlap), results = "asis"}
cat("## Cross-population reproducibility\n\n")
cat("Top-5% edge sets: overlap proportion (shared / top-k of A) and Jaccard index (shared / union); edge presence in each network.\n\n")
print(knitr::kable(top_overlap(A, B), digits = 3))
both <- edge_list(A)[, .(cause, effect, strength_A = strength)][, strength_B := as.vector(B)]
k <- round(0.05 * length(A))
cat("\n\n### Relationships in the top 5% of both networks\n\n")
topA <- both[order(-strength_A)][seq_len(k)]
topB <- both[order(-strength_B)][seq_len(k)]
print(knitr::kable(topA[paste(cause, effect) %in% paste(topB$cause, topB$effect)], digits = 2))
```
