---
title: "Directed Granger-causal network: `r params$analysis`"
output:
  html_document:
    toc: true
    toc_float: true
params:
  analysis: "baseline"
  results_dir: "../results"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10)
source("../R/analysis_functions.R")
model <- read_model(file.path(params$results_dir, "models", params$analysis),
                    file.path(params$results_dir, "sequences", params$analysis))
A <- model$A
```

Edges are directed Granger-causal relationships: a non-zero integrated
excitation from *A* to *B* means that past occurrences of *A* improve the
prediction of future occurrences of *B* given the histories of all other
modelled event types. They are not estimates of interventional causal effects.

## Cohort

```{r}
knitr::kable(t(model$cohort), col.names = "value")
```

## Network summary

```{r}
knitr::kable(network_summary(A))
```

## Ten strongest directed relationships

```{r}
knitr::kable(top_edges(A, 10))
```

## Weighted in- and out-degree

```{r}
knitr::kable(degree_table(A))
```

## Excitation matrix

Rows: source disease; columns: target disease. Asterisks mark the ten strongest connections.

```{r, fig.height = 9}
plot_heatmap(A)
```

## Network

Split at the 75th percentile of edge strength for graphical reasons only.
Node size is proportional to the weighted in-degree; edge width to the excitation strength.

```{r, fig.height = 6, fig.width = 14}
plot_network(A)
```

## Excitation kernels

The six strongest relationships excluding self-excitation.

```{r, fig.height = 6}
plot_kernels(model, 6)
```
